Trauma treatment delay

### 2023-10-27 manuscriptlongversion.Rmd
code
text

The outcome is delayed treatment, which is defined as more than 30
minutes passing from arrival before receiving treatment, as identified
by the multidisciplinary review board and recorded in the trauma care
quality database.

@@

>>>>

The outcome is delayed treatment, which is defined as more than 30
minutes passing from arrival before receiving treatment, as identified
by the multidisciplinary review board and recorded in the trauma care
quality database. The independent variables are gender, patient survival
after 30 days from admission, highest hospital care level, GCS on
arrival, respiratory rate on arrival, systolic blood pressure on
arrival, time from arrival at the hospital until first computed
tomography, if the patient was intubated on arrival and whether they
arrived during weekend or working hours. Those are used as factor
variables. ISS and age are used as continuous variables.

@@

Rstudio was used to perform the logistical regression. The dependent
variable is OFI_delay, which is the presence of the ofi delayed
treatment.

## Ethical considerations

Ethical permit is required and exists. The ethical review number is
2021-02541 and 2021-03531. An ethical problem that might be brought up
is the anonymity of the patients. In the registry, patients social
security number is present and could theoretically be used to identify
the patient in question. This will not be a problem though, as in the
analysis, the social security number is removed from the data before the
logistical regression is ran. Furthermore, the results will be presented
with patients grouped together, not individually. This will make it
impossible for anyone to identify patients. During the analysis, a VPN
was used to access the database to ensure that no data was leaked or
used for other purposes.
